dyngen: simulating developing single cells

### 2019-08-28 content.tex
update

\begin{figure}[hb]
	\centering
	\includegraphics[width=\linewidth]{fig/showcase_3.png} 
	\caption{Showcase of dyngen functionality. \textbf{TODO: change to pdf.} Remove B?} % TODO: update label
	\label{fig:dyngen}
\end{figure}

@@

\begin{figure}[hb]
	\centering
	\includegraphics[width=\linewidth]{fig/simplecyclic_edited} 
	\caption{Showcase of dyngen functionality. A time resolution of 0.1 was used, but this can be increased or decreased without effect on performance of the execution of the simulation. \textbf{TODO: perhaps it's better to replace Figure \ref{fig:simplecyclic} with one subfigure for each of the paragraphs in this text.}}
	\label{fig:simplecyclic}
\end{figure}

@@

dyngen's approach was inspired by GeneNetWeaver's \cite{schaffter_genenetweaversilicobenchmark_2011} workflow to generate \textit{in silico} bulk profiles for evaluating network inference methods \cite{marbach_wisdomcrowdsrobust_2012}. The workflow to generate \textit{in silico} single cell data consists of six main steps: 1. define the module network, 2. generate gene regulatory network, 3. convert regulatory interactions to biochemical reactions, 4. simulate the developmental backbone, 5. simulate single cells, and 6. simulate experiment.

@@

To simulate certain trajectory topologies, we therefore designed module networks in which the cells follow a particular trajectory topology given certain parameters.
\subsubsection{Predefined backbones}
\subsubsection{Backbone lego}

\subsection{Generate gene regulatory network}
\subsubsection{Generate the transcription factor network}
\subsubsection{Generate targets and housekeeping genes}

\subsection{Convert gene regulatory network to a set of reactions}

\subsection{Simulate developmental backbone}

\subsection{Simulate single cells}
\subsubsection{Map SSA simulations to backbone}

\subsection{Simulate experiment}
\subsubsection{Snapshot experiment}
\subsubsection{Time series experiment}
\subsubsection{Perturbation experiment}

>>>>

\begin{figure}[htb!]
	\centering
	\includegraphics[width=\linewidth]{fig/showcase_3.png} 
	\caption{Showcase of dyngen functionality. \textbf{TODO: change to pdf.} Remove B?} % TODO: update label
	\label{fig:dyngen}
\end{figure}

@@

\begin{figure}[htb!]
	\centering
	\includegraphics[width=\linewidth]{fig/simplecyclic_edited} 
	\caption{Showcase of dyngen functionality. A time resolution of 0.1 was used, but this can be increased or decreased without effect on performance of the execution of the simulation. \textbf{TODO: perhaps it's better to replace Figure \ref{fig:simplecyclic} with one subfigure for each of the paragraphs in this text.}}
	\label{fig:simplecyclic}
\end{figure}

@@

dyngen's approach was inspired by GeneNetWeaver's \cite{schaffter_genenetweaversilicobenchmark_2011} workflow to generate \textit{in silico} bulk profiles for evaluating network inference methods \cite{marbach_wisdomcrowdsrobust_2012}. The workflow to generate \textit{in silico} single cell data consists of six main steps (Figure \ref{fig:explain_methods}).

\begin{figure}[htb!]
	\centering
	\includegraphics[width=\hugefigure]{fig/explain_methods} 
	\caption{The workflow of dyngen.}
	\label{fig:explain_methods}
\end{figure}

@@

In dyngen, the behaviour of the dynamic process is determined in the way that modules are regulating each other, where each module is a set of coregulated genes. By carefully designing the module network, the desired dynamic behaviour can be achieved. A module may have basal expression, which means that pre-mRNA of the genes in this module will be transcribed without the presence of transcription factor molecules. 
Basal expression
Burn phase

Several examples of module networks are given (Figure \ref{fig:example_backbones}). A linear process can by achieved by simply chaining together several modules. A cyclic process is a chain of modules, where the last module represses the first module. A bifurcating process consists of two modules that repress each other, and some modules leading up to and resulting from the bifurcation. A converging 
Note that these examples represent the bare minimum in terms of number of modules used. Using more modules is typically desired, since some transitions will otherwise occur too quickly.

\begin{figure}[htb!]
	\centering
	\includegraphics[width=\LARgefigure]{fig/example_backbones} 
	\caption{Example module networks}
	\label{fig:example_backbones}
\end{figure}

\subsubsection{Backbone lego}
\blindtext

\subsubsection{Predefined backbones}
\blindtext

\subsection{Generate gene regulatory network}
\blindtext
\subsubsection{Generate the transcription factor network}
\blindtext
\subsubsection{Generate targets and housekeeping genes}
\blindtext

\subsection{Convert gene regulatory network to a set of reactions}
\blindtext

\subsection{Simulate developmental backbone}
\blindtext

\subsection{Simulate single cells}
\blindtext

\subsubsection{Map SSA simulations to backbone}
\blindtext

\subsection{Simulate experiment}
\blindtext

\subsubsection{Snapshot experiment}
\blindtext

\subsubsection{Time series experiment}
\blindtext

\subsubsection{Perturbation experiment}
\blindtext
